FraCaS: 80 percent complete

### 2019-02-25 paper2018/paper.tex
acl formatting

\documentclass{article}
\usepackage{todonotes}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

\usepackage[backend=bibtex,citestyle=authoryear,style=alphabetic,natbib]{biblatex}
\addbibresource{PaperTools/bibtex/jp.bib}
\addbibresource{phorae.bib}
\addbibresource{IWCSbib.bib}

@@

\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether an NL hypothesis H follows from an NL premise(s) P. NLI has received a lot of attention in the Computational Semantics literature and has been approached using a variety of techniques, ranging from logical approaches  \citet{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017} all the way to the recent Deep Learning (DL) models for NLI. The latter approaches, following the general trend in NLP, have been dominating NLI and indeed a number of impressive results have been produced \citet{kim:2018,radford:2018,liu:2019}.\footnote{These are the three systems with the best results on SNLI in increasing order.} State-of-the-art DL systems achieve an accuracy of around 0.9 when tested on suitable datasets. However, the datasets that are used are assuming a definition of inference that can be thought to be `looser' or less precise compared to the definition assumed in platforms that used to test logical approaches. Consider the following two examples, one from the SNLI dataset, predominatly used to test DL approaches and which has a state-of-the-art performace of 0.911 \citet{lui:2019'}, and the FraCaS test suite, the dataset \textit{par excellence} to test logical approaches.

@@

\begin{figure}
  \centering
{
  \tiny
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.7cm,
                    semithick]
  \tikzstyle{every state}=[draw=black,text=black,shape=rectangle,text width=2cm]

@@

  \path
  (Syntax) edge (GF)
  (Sem) edge (Hask)
  (Hyper) edge (Coq);
\end{tikzpicture}
}
\caption{Phases in our system. ($\ast$) At the level of Coq, we handle
  the details of the adverbial (veridicality properties) and
  adjectival semantics (division into subsective, extentional,
  non-committal, etc. categories.) }
  \label{fig:overview}
\end{figure}

@@

FraCaS intends to classify each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  In this work,
we have amended the FraCaS suite to correct a few problems. First,
certain test case are not formed correctly. Those were already
identified by Bill MacCartney\todo{cite} as such (using an ``undef''
labelling), and we removed those. Second, a few test cases occur twice
in the suite, but with two different labelling (one YES and one UNK),
with an annotation that those labellings correspond to different
readings. However, elsewhere in the suite, if a problem has several
readings but only one has entailment, it occurs only once and is
marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. We have also
removed case 199 (which appears to be vacuous). Finally we changed the
labelling of the following cases, which appeared to have been
misclassified. We note that the majority of the mistaken
classifications occur in sections 3 and 4, which have not been
previously attempted and thus, we propose, have not been properly
scrutinized.

\begin{center}
\begin{tabular}{ccc}
 test case & new class & comment \\ \hline
    005 & UNK & missing hypothesis: there are italian tenors \\
   056 &  Yes & Already identified as such by MacCartney \\
  069 & Unk & Mary could have used someone else's workstation \\
  119 & Unk & \textit{ibid.} \\
  181 & Yes & for the same reason as 180 \\
  226 & Yes &
\end{tabular}
\end{center}

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & {\kern -1em} \# cases & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
7 & Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases shown in the
    third column, the actual number of test cases attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}. A dash indicates that no attempt was made
    for a given section. }
  \label{tbl:results}
\end{table}

Table \ref{tbl:results} shows a considerable improvement over earlier
approaches in terms of coverage, with three more sections covered over
previous state of the art. We thus cover 259 out of 337 cases (77\%),
compared to at most 174 cases (52\%) in previous work. Additionally,
our system performs generally the best in terms of accuracy. In
particular, section 6 sees a large improvement in accuracy, which we
attribute to our new analysis of comparatives, enabled by our dynamic
semantics.

@@

\printbibliography

>>>>

\documentclass[11pt]{article}
\usepackage{acl2019}
\usepackage{todonotes}
\usepackage{tikz}
\usetikzlibrary{arrows,automata}

@@

\maketitle{}

\begin{abstract}
  TODO
\end{abstract}
\section{Introduction}
Natural Language Inference (NLI) is the task of determining of whether an NL hypothesis H follows from an NL premise(s) P. NLI has received a lot of attention in the Computational Semantics literature and has been approached using a variety of techniques, ranging from logical approaches  \citet{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017} all the way to the recent Deep Learning (DL) models for NLI. The latter approaches, following the general trend in NLP, have been dominating NLI and indeed a number of impressive results have been produced \citet{kim:2018,radford:2018,liu:2019}.\footnote{These are the three systems with the best results on SNLI in increasing order.} State-of-the-art DL systems achieve an accuracy of around 0.9 when tested on suitable datasets. However, the datasets that are used are assuming a definition of inference that can be thought to be `looser' or less precise compared to the definition assumed in platforms that used to test logical approaches. Consider the following two examples, one from the SNLI dataset, predominatly used to test DL approaches and which has a state-of-the-art performace of 0.911 \citet{lui:2019'}, and the FraCaS test suite, the dataset \textit{par excellence} to test logical approaches.

@@

\begin{figure*}
  \centering
{
  \tiny
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.7cm,
                    semithick]
  \tikzstyle{every state}=[draw=black,text=black,shape=rectangle,text width=2cm]

@@

  \path
  (Syntax) edge (GF)
  (Sem) edge (Hask)
  (Hyper) edge (Coq);
\end{tikzpicture}
}
\caption{Phases in our system. ($\ast$) At the level of Coq, we handle
  the details of the adverbial (veridicality properties) and
  adjectival semantics (division into subsective, extentional,
  non-committal, etc. categories.) }
  \label{fig:overview}
\end{figure*}

@@

FraCaS intends to classify each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  In this work,
we have amended the FraCaS suite to correct a few problems. First,
certain test case are not formed correctly. Those were already
identified by Bill MacCartney\todo{cite} as such (using an ``undef''
labelling), and we removed those. Second, a few test cases occur twice
in the suite, but with two different labelling (one YES and one UNK),
with an annotation that those labellings correspond to different
readings. However, elsewhere in the suite, if a problem has several
readings but only one has entailment, it occurs only once and is
marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. We have also
removed case 199 (which appears to be vacuous). Finally we changed the
labelling of the cases listed in Table \ref{tab:overrulings}, which appeared to have been
misclassified. We note that the majority of the mistaken
classifications occur in sections 3 and 4, which have not been
previously attempted and thus, we propose, have not been properly
scrutinized.
\begin{table*}
  \centering
\begin{tabular}{ccc}
 test case & new class & comment \\ \hline
    005 & UNK & missing hypothesis: there are italian tenors \\
   056 &  Yes & Already identified as such by MacCartney \\
  069 & Unk & Mary could have used someone else's workstation \\
  119 & Unk & \textit{ibid.} \\
  181 & Yes & for the same reason as 180 \\
  226 & Yes &
\end{tabular}
  \caption{Overruled FraCaS cases}
  \label{tab:overrulings}
\end{table*}

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table*}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & {\kern -1em} \# cases & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
7 & Temporal     & 75          &  -       &   -    &   -  &  -   &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 337         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of test cases shown in the
    third column, the actual number of test cases attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}. A dash indicates that no attempt was made
    for a given section. }
  \label{tab:results}
\end{table*}

Table \ref{tab:results} shows a considerable improvement over earlier
approaches in terms of coverage, with three more sections covered over
previous state of the art. We thus cover 259 out of 337 cases (77\%),
compared to at most 174 cases (52\%) in previous work. Additionally,
our system performs generally the best in terms of accuracy. In
particular, section 6 sees a large improvement in accuracy, which we
attribute to our new analysis of comparatives, enabled by our dynamic
semantics.

@@

\bibliography{PaperTools/bibtex/jp.bib,phorae.bib,IWCSbib.bib}

\bibliographystyle{acl_natbib}
